\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother


\date{}

\begin{document}

\newcommand*{\affaddr}[1]{#1}

\% Make title large and bold

\title{\Large\bfseries IPAC Postdoctoral Application Guide}
\author{
    Weidong Zhang\thanks{E-mail: wdzhang@sjtu.edu.cn}\\
IPAC, SJTU\thanks{Homepage: http://automation.sjtu.edu.cn/ipac}\\
\today
}

\maketitle

In China, postdoc is a special 2-5 year position. The application has to
be approved by 4 aspects:

\begin{itemize}
\tightlist
\item
  \textbf{Host professor} (The host professor makes the decision);
\item
  \textbf{Department} (The host professor prepares materials for
  checking);
\item
  \textbf{University Postdoc Administration Office} (The host professor
  prepares materials for checking);
\item
  \textbf{State Postdoc Administration Committee} (The website form you
  fill in).
\end{itemize}

\hypertarget{stages}{%
\subsection{Stages}\label{stages}}

There are \textbf{5 stages} you should move through:

I. Supervisor contact (1-3 weeks).

\begin{itemize}
\tightlist
\item
  Contact with \textbf{Prof.~Weidong Zhang} for your application of
  postdoc and research proposal.
\item
  Prof.~Zhang may arrange different professors of his group as your
  supervisor.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Online postdoctoral application (1-3 weeks).
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Complete \textbf{online forms} and prepare \textbf{documents} required
  by SJTU.
\item
  You need to determine your arriving time and residence time.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{2}
\tightlist
\item
  Confirmation of the terms and conditions.
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Sign contract afterwards with electronic signature, or in scanned
  copy.
\end{itemize}

\begin{enumerate}
\def\labelenumi{\Roman{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Visa and Residence Permit Application.
\end{enumerate}

\begin{itemize}
\tightlist
\item
  Z visa would take 3 weeks to issue, which permits your entry to China.
\item
  Residence permit should be applied after your arrival.
\end{itemize}

V. Accommodation application.

\begin{itemize}
\tightlist
\item
  How long it would take is hard to estimate yet.
\item
  If the accommodation has been approved, you need to PAY for your
  absence.
\end{itemize}

\hypertarget{instructions}{%
\subsection{Instructions}\label{instructions}}

Click \href{Instructions_on_stage_2.md}{HERE} for instructions on stage
II.

Click \href{Instructions_on_stage_4.md}{HERE} for instructions on stage
IV.

\hypertarget{contact-us}{%
\subsection{Contact us}\label{contact-us}}

For problems in stages I and III, please contact
\href{mailto:wdzhang@sjtu.edu.cn}{Prof.~Zhang}.

For problems in other stages, please contact
\href{mailto:598053117@qq.com}{Zehua Jia} and
\href{mailto:zzw1993@sjtu.edu.cn}{Zhiwei Zhuang}.

\href{mailto:wdzhang@sjtu.edu.cn}{Weidong Zhang}

\href{http://automation.sjtu.edu.cn/ipac}{IPAC, SJTU}

You may also refer to the on-line guide
\href{https://github.com/kouyx/ipac-postdoc-guide/blob/master/README.md}{HERE}.

\end{document}
